Tor's Usability for Censorship Circumvention

### 2015-12-11 paper/circumvention-experiment.tex
put back changes Nathan made I accidentally blew away on merge

After users complete the browsing tasks (or time runs out), we conducted an
interview asking participants about their censorship circumvention experience.
We were able to tailor the interview to the particular participant, since we were able to
observe our participants' sessions. This way, we could follow up and ask participants
about reasons for taking particular actions and verify any hypothesis we had about 
the participant (such as ``they didn't know what to do on window 3'').  We did
ask a couple question across all participants: 
``What was the most challenging part of connecting?''
and
``What is one change you would recommend?''

@@

A progress indicator at the top of the window indicates various steps necessary
for configuring a connection. In addition to communicating to the user what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately. In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
In the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor Browser. Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make. We hope that our work is able to help people more easily access the free Internet.

>>>>

After users completed the browsing tasks (or time ran out), we conducted an
interview asking participants about their censorship circumvention experience.
We were able to tailor the interview to the particular participant, since we were able to
observe our participants' sessions. This way, we could follow up and ask participants
about reasons for taking particular actions and verify any hypothesis we had about 
the participant (such as ``they didn't know what to do on window 3'').  We did
ask a couple question across all participants: 
``What was the most challenging part of connecting?''
and
``What is one change you would recommend?''

@@

A progress indicator at the top of the window indicates various steps necessary
for configuring a connection. In addition to communicating to the user what the various 
steps of configuration are from the beginning, this indicator also serves to clarify the independence of
bridges and proxies, which need to be configured separately.

In the event of a failure, the user is
returned to the first step of the process -- the bridge configuration -- to
avoid misleading users into thinking the proxy settings are the culprit. Previously,
the user had to manually click to go backward in the dialog to configure bridges.
In the rare event that the proxy is the issue for the connection setting, the user
will be directed to the proxy page naturally through the flow of the UI. \\

@@

\noindent {\bfseries s} We will help incorporate changes into the Tor Browser. Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make. We hope that our work is able to help people more easily access the free Internet.
